
##What is mean total number of steps taken per day?

```{r}
rawdata <- read.csv("activity.csv", na.strings = c("NA"))
result <- aggregate(steps ~ date, data = rawdata, sum)
hist(result$steps)
```

Mean is: 
```{r}
mean(result$steps)
```

Median is:
```{r}
median(result$steps)
```



##What is the average daily activity pattern?

Time series plot of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)
```{r}
MeanStepsAcrossIntervals <- aggregate(steps ~ interval, data = rawdata, mean)
plot(MeanStepsAcrossIntervals$interval, MeanStepsAcrossIntervals$steps, type = "l")
```


Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?
```{r}
MeanStepsAcrossIntervals[which.max(MeanStepsAcrossIntervals$steps),"interval"]
```


##Imputing missing values

Calculate and report the total number of missing values in the dataset
```{r}
length(which(is.na(rawdata$steps)))
```

Devise a strategy for filling in all of the missing values in the dataset. Create a new dataset that is equal to the original dataset but with the missing data filled in.

I'll take means for 5-min intervals as target values.

```{r}
EnrichedData = cbind(rawdata)
for (row in 1:nrow(EnrichedData)) {
  if (is.na(EnrichedData$steps[row])) {
    matchingdata = which(MeanStepsAcrossIntervals$interval == EnrichedData$interval[row])
    EnrichedData$steps[row] <- MeanStepsAcrossIntervals[matchingdata[1],"steps"]
  }
}
```

Make a histogram of the total number of steps taken each day
```{r}
resultEnrichedData <- aggregate(steps ~ date, data = EnrichedData, sum)
hist(resultEnrichedData$steps)
```

Mean is: 
```{r}
mean(resultEnrichedData$steps)
```

Median is:
```{r}
median(resultEnrichedData$steps)
```

##Are there differences in activity patterns between weekdays and weekends?

Create a new factor variable in the dataset with two levels – “weekday” and “weekend” indicating whether a given date is a weekday or weekend day.
```{r}
NewData = cbind(EnrichedData)
NewData$DateAsDate <- strptime(NewData$date, "%Y-%m-%e")
NewData$WeekdayNo <- ifelse(format(NewData$DateAsDate, "%u") %in% c(6,7), "weekend", "weekday")
NewData$WeekdayNo <- factor(NewData$WeekdayNo)
```

Make a panel plot containing a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all weekday days or weekend days (y-axis).

```{r}
WeekdayMeans <- aggregate(steps ~ interval, data = subset(NewData, WeekdayNo == "weekday"), mean)
plot(WeekdayMeans$interval, WeekdayMeans$steps, type = "l", main = "Weekdays")
```

```{r}
WeekendMeans <- aggregate(steps ~ interval, data = subset(NewData, WeekdayNo == "weekend"), mean)
plot(WeekendMeans$interval, WeekendMeans$steps, type = "l", main = "Weekends")

```


